\documentclass[a4paper,12pt]{article}

\newcount\totalrating % for Lua code to write to later
\directlua{dofile("score-table.lua")}
\newcommand\soft{slop}

% for S19/D19 charts
\newcommand\singlechart[1]{\directlua{singlechart(#1)}}
\newcommand\doublechart[1]{\directlua{doublechart(#1)}}
% for 20/21 charts
\newcommand\fullchart[1]{\directlua{fullchart(#1)}}
% co-op charts have much more reason to list the tier-list placements,
% so have a separate system for them
\newcommand\coopchart[1]{\directlua{coopchart(#1)}}


\begin{document}
This is a port of my \textit{Pump It Up} title-tracking spreadsheet to \LaTeX.
I began this project when I found out that Apple was deprecating Numbers 14.5 in favor of a subscription-based service that sounds a lot like why I don't care for Micro\soft\ Excel.

There's just one more thing to bring up: most of my recent plays are on a machine that hasn't had the opportunity to upgrade to \textit{Pump It Up Phoenix}, which means that the title on my actual AM.PASS card is still ``Intermediate Lv.~9''.
Scores achieved on XX are converted to Phoenix grades by taking a picture of the results screen, adding or subtracting to the perfect count based on the changes Phoenix made to hold-tick counts in the chart, and ignoring the max combo.
The result is almost always accurate, especially seeing as the only song you're \textit{likely} to drop holds in is 8~6~S20, which doesn't have any hold-tick changes to begin with.
This means that large miss-count differences aren't really of concern and the only problem is that I can't know where the maximum combo starts and ends; this makes less than 1000 points of difference in most cases.

%Without further ado, I've been trying to also get the ``Intermediate Lv.~10'' title requirements with only S19s:\\
%\singlechart{19}\\
%...and with only D19s:\\
%\doublechart{19}\\

\begin{table}[htbp]
\fullchart{20}
\end{table}

\fullchart{20,true}
I have \the\numexpr13000-\totalrating\ points left to get to Advanced Lv.~1, or about \the\numexpr(13000-\totalrating)/650\ more 20 clears; in other words, I'm \the\numexpr\totalrating/130\% of the way there. Promising stuff, I suppose?

\begin{table}[htbp]
\fullchart{21}
\end{table}

\fullchart{21,true}
Advanced~4 requires you to already have Advanced~3, but it's nice being \the\numexpr\totalrating/150\% of the way there even before that.

\begin{table}[htbp]
\coopchart{nil}
\end{table}

\coopchart{true}
Co-op titles are a lot harder to get, because you have to convince people to play them on your card, and there are like five people I've met that can play the easiest co-op charts to begin with (they start at about D10).
I'm only \the\numexpr\totalrating/300\% towards Co-Op Lv.~1.

\end{document}